---
title: "tspec"
output: pdf_document
---

Tissuespecific by effect:
```{r setup, include=FALSE}

library('knitr')
knitr::opts_chunk$set(cache=TRUE)
opts_chunk$set(fig.path = "/Users/sarahurbut/Dropbox/PaperEdits/Paper/Figures/") 
```

```{r barplotspec,echo=FALSE}
source("../Analysis/normfuncs.R")
thresh=0.05

lfsr.mash=read.table("../Results_Data//withzerolfsr.txt")[,-1]
pm.mash=as.matrix(read.table("../Results_Data/withzeroposterior.means.txt")[,-1])
standard.error=read.table("../Data/standard.error.txt")
pm.mash.beta=pm.mash*standard.error
maxz=read.table("../Data/maxz.txt")
maxb=read.table("../Data/maxbetahats.txt")

nsig=rowSums(lfsr.mash<thresh)
pm.mash.beta.norm=het.norm(effectsize = pm.mash.beta)
pm.mash.beta.norm=pm.mash.beta.norm[(nsig>0),]
lfsr.mash=as.matrix(lfsr.mash[nsig>0,])
colnames(lfsr.mash)=colnames(maxz)

thresh=0.05
missing.tissues=c(7,8,19,20,24,25,31,34,37)
color.gtex=read.table("../Data/GTExColors.txt",sep = '\t', comment.char = '')[-missing.tissues,]
col = as.character(color.gtex[,2])

barplot(apply(lfsr.mash[which(rowSums(lfsr.mash<=thresh)==1),],2,function(x){sum(x<=thresh)}),las=2,cex.names=0.3,#main=paste0("Number of eQTL with LFSR<",0.05," in Single Tissue"),
        ylim=c(0,500),col=col)


###Now plot the number of normalized effects greater than 0.5 for each tissue, given that those effects were significant in at least one tissue
#barplot(apply(pm.mash.beta.norm[which(rowSums(pm.mash.beta.norm>0.5)==1),],2,function(x){sum(x>0.5)}),las=2,cex.names=0.5,main=paste0("Number of eQTL with Bjnorm>0.5 in Single Tissue"),ylim=c(0,500))



###Now plot the number of normalized effects greater than 0.5 for each tissue, given that those effects were significant in that tissue

a=which(rowSums(pm.mash.beta.norm>0.5)==1)
lfsr.fold=as.matrix(lfsr.mash[a,])
pm=as.matrix(pm.mash.beta.norm[a,])
tspec=NULL
for(i in 1:ncol(pm)){
  #tspec[i]=sum(lfsr.fold[,i]<0.05&pm[,i]>0.5)
  tspec[i]=sum(pm[,i]>0.5)
  }##check to see that the effect is significant and greater than 0.5 max effect in only that tissue

tspec=as.matrix(tspec);rownames(tspec)=colnames(maxz)

barplot(as.numeric(t(tspec)),#main=paste0("Number of eQTL with Bjnorm>0.5 in one Tissue"),
        las=2,cex.names=0.3,col=col,names=colnames(lfsr.fold))
```

With pdf function:

```{r withpdf}

pdf("~/Dropbox/PaperEdits/Paper/Figures/tspecbynumber.pdf")

barplot(apply(lfsr.mash[which(rowSums(lfsr.mash<=thresh)==1),],2,function(x){sum(x<=thresh)}),las=2,cex.names=0.3,#main=paste0("Number of eQTL with LFSR<",0.05," in Single Tissue"),
        ylim=c(0,500),col=col)

dev.off()

###Now plot the number of normalized effects greater than 0.5 for each tissue, given that those effects were significant in at least one tissue
#barplot(apply(pm.mash.beta.norm[which(rowSums(pm.mash.beta.norm>0.5)==1),],2,function(x){sum(x>0.5)}),las=2,cex.names=0.5,main=paste0("Number of eQTL with Bjnorm>0.5 in Single Tissue"),ylim=c(0,500))



###Now plot the number of normalized effects greater than 0.5 for each tissue, given that those effects were significant in that tissue

a=which(rowSums(pm.mash.beta.norm>0.5)==1)
lfsr.fold=as.matrix(lfsr.mash[a,])
pm=as.matrix(pm.mash.beta.norm[a,])
tspec=NULL
for(i in 1:ncol(pm)){
  #tspec[i]=sum(lfsr.fold[,i]<0.05&pm[,i]>0.5)
  tspec[i]=sum(pm[,i]>0.5)
  }##check to see that the effect is significant and greater than 0.5 max effect in only that tissue

tspec=as.matrix(tspec);rownames(tspec)=colnames(maxz)

pdf("~/Dropbox/PaperEdits/Paper/Figures/tspecbymag.pdf")

barplot(as.numeric(t(tspec)),#main=paste0("Number of eQTL with Bjnorm>0.5 in one Tissue"),
        las=2,cex.names=0.3,col=col,names=colnames(lfsr.fold))

dev.off()