\section*{Introduction}
Variation in gene expression is an important mechanism underlying susceptibility to complex disease.

The simultaneous genome-wide assay of gene expression and genetic variation allows the mapping of the genetic factors that underpin individual differences in quantitative levels of expression (expression QTLs; eQTLs). 
The availability of this information provides immediate insight into a biological basis for disease associations identified through genome-wide association (GWA) studies, and can help to identify networks of genes 
involved in disease pathogenesis (\cite{nicolae_trait-associated_2010, veyrieras_high-resolution_2008}).
Available methods are limited not only in their ability to {\it jointly analyze data on all tissues} to maximize power, but also in simultaneously {\it allowing for both qualitative and quantitative differences among eQTLs} present in each tissue.

Initial approaches to quantify the effect of a particular SNP on gene expression considered only one tissue at a time, and ignored the effect of the SNP on gene expression in other tissues.
This fails to exploit the power of  shared genetic variation in effects on expression - i.e. the information that the effect of the gene-snp pair in one tissue can provide about the effect in another- and limits our understanding of multiple-tissue phenotypes.
Furthermore, even past attempts at quantifying heterogeneity of eQTLs using the data across tissues jointly were limited in both the number of tissues considered, and also the level of heterogeneity considered. Qualitative heterogeneity refers to calling a snp `active' or `inactive' in a given tissue. For example, previous work has referred to the setting in which the gene-snp pair is active in all tissues as `shared' and active in only one as 'tissue-specific'  (\cite{flutre_statistical_2013,wen_bayesian_2014}).
However, a QTL may be `active' in all or many tissues and with varying magnitude or sign; we refer to this as quantitative heterogeneity.
 Indeed, our initial motivation came from our analysis of GTEx pilot data, in which we see evidence that many $(50\%)$ QTLs are shared across all nine tissues. In this context, a QTL is called based on whether it demonstrates significant posterior probability of being active in a particular tissue. Applying our hierarchical model to the dataset from Dimas {\it et al} \cite{dimas_common_2009} with 3 tissues, we found just 8\% of eQTLs are specific to a single tissue, with an estimated 88\% of eQTLs being common to fibroblasts, LCL cells and T-Cells \cite{flutre_statistical_2013}. Not all eQTLs are shared by all tissues; some tissues may share eQTLs more than others. To allow for this, our previous hierarchical model attempted to infer the extent of such sharing by estimating the proportion of eQTL which were shared in various `configurations' or patterns of binary activity in which a QTL was `called' or `absent' in each tissue.
 However, these binary configurations are still \textit{limited in their ability to capture continuous variation} in levels of activity among tissues in which the SNP is considered active. 
 In fact, as the number of tissues considered increases, perhaps the more interesting and biologically relevant question becomes one of quantitative heterogeneity - that is, how do the patterns of effect vary across tissues in which the SNP is called `active'.  
Quantifying the effect sizes of the gene-snp pair across tissues considering the evidence contained in all tissues jointly thus reveals new patterns of activity across tissues, which differ in their relationship in sign and magnitude within and between tissues. Thus effects can be `shared' but not `consistent' across tissues. The structure of this paper is as follows: we will describe our approach in brief for modeling and estimating these effect sizes across tissues, demonstrate the utility of such an approach on simulated data, and apply our method to data from the GTEX dataset, version 6.0, where we analyze effects size for 16,069 genes across 44 tissues.
