---
title: "expranalysisold"
output: html_document
---


Check to see if the QTLs have expression values that are tissue-specific.

```{r, cache=TRUE,echo=FALSE}
library('knitr')

opts_chunk$set(fig.path = "/Users/sarahurbut/Dropbox/PaperEdits/Paper/Figures/") 

library('qtlcharts')
data=read.csv("~/Dropbox/AvgExpr.csv",header = T)
rownames(data)=data[,1]
expr.data=data[,-1]
maxz=read.table("../Data/maxz.txt")
qtl.names=sapply(1:length(rownames(maxz)),function(x){unlist(strsplit(rownames(maxz)[x], "[_]"))[[1]]})
expr.sort=expr.data[rownames(expr.data)%in%qtl.names,]

lfsr=read.table("../Data/Aug13withEDlfsr.txt")[,-1]
pmash=read.table("../Data/Aug13withEDposterior.means.txt")[,-1]


colnames(lfsr)=colnames(pmash)=colnames(maxz)
rownames(lfsr)=rownames(pmash)=rownames(maxz)

a=match(qtl.names,rownames(expr.sort))###in order to make sure the gene names are the same in both


expr.sort=expr.sort[a,]

head(rownames(expr.sort))[1:5]
head(rownames(lfsr))[1:5]
missing.tissues=c(7,8,19,20,24,25,31,34,37)
exp.sort=expr.sort[,-missing.tissues]
colnames(exp.sort)=colnames(maxz)
```

```{r definefunc}
plot_tissuespecific = function(tissuename,lfsr,curvedata,title,thresh=0.05,subset=1:44){
  index_tissue=which(colnames(lfsr) %in% tissuename);
  ybar=title
  ##create a matrix showing whether or not lfsr satisfies threshold
  sigmat = lfsr <= thresh;
  sigs=which(rowSums(sigmat[,index_tissue,drop=FALSE])==length(tissuename) & rowSums(sigmat[,-index_tissue,drop=FALSE])==0)
  sigs.it=which(lfsr[sigs,index_tissue]<thresh)
  iplotCurves(curvedata[sigs,subset],chartOpts=list(curves_xlab="Tissue",curves_ylab=ybar))
}  


plot_tissuespecifictwo = function(tissuename,lfsr,curvedata,title,thresh=0.05,subset=1:44,exclude=0.01){
  index_tissue=which(colnames(lfsr) %in% tissuename);
  ybar=title
  ##create a matrix showing whether or not lfsr satisfies threshold
  sigmat = lfsr <= thresh;
  sigs=which(rowSums(sigmat[,index_tissue,drop=FALSE])==length(tissuename) & rowSums(sigmat[,-index_tissue,drop=FALSE])==0)
  #sigs.it=which(lfsr[sigs,index_tissue]<thresh)
  #iplotCurves(curvedata[sigs,subset],chartOpts=list(curves_xlab="Tissue",curves_ylab=ybar))
  #norm=curvedata[sigs,]/curvedata[sigs,index_tissue]
  #boxplot(norm,las=2)
  norm.spec=t(apply(curvedata[sigs,],1,function(x){x[index_tissue]/x}))
  norm.other=t(apply(curvedata[-sigs,],1,function(x){x[index_tissue]/x}))
  summary(unlist(as.numeric(norm.spec)))
  summary(unlist(as.numeric(norm.other)))
  norm.other=unlist(as.numeric(norm.other))
  norm.spec=unlist(as.numeric(norm.spec))
  upper.quant=quantile(norm.spec, 1-exclude);lower.quant=quantile(norm.spec, exclude);
  upper.quant.other=quantile(norm.other, 1-exclude);lower.quant.other=quantile(norm.other, exclude);
  xmin=min(lower.quant,lower.quant.other)
  xmax=max(upper.quant,upper.quant.other)
plot(density(as.numeric(norm.other[norm.other<upper.quant.other&norm.other>=lower.quant.other])),
     ,#,nclass=1000,freq=F,
     main=paste0("Non",tissuename,"SpecificGenes"),xlim=c(xmin,xmax))
lines(density(as.numeric(norm.spec[norm.spec<upper.quant&norm.spec>=lower.quant])),col="red",main=paste0(tissuename,"SpecificGenes"))
 
#   hist(as.numeric(norm.other[norm.other<upper.quant.other&norm.other>=lower.quant.other]),nclass=1000,freq=F,xlim=c(xmin,xmax))
} 

compare.distribution=function(tissuename,curvedata,lfsr,thresh=0.05){
    index_tissue=which(colnames(lfsr) %in% tissuename);
    sigmat = lfsr <= thresh;
  sigs=which(rowSums(sigmat[,index_tissue,drop=FALSE])==length(tissuename) & rowSums(sigmat[,-index_tissue,drop=FALSE])==0)
  norm.spec=t(apply(curvedata[sigs,],1,function(x){x[index_tissue]/x}))##divide special tissue by other tissue effects for numsigxR matrix
  norm.other=t(apply(curvedata[-sigs,],1,function(x){x[index_tissue]/x}))

  norm.other=unlist(as.numeric(norm.other))
  norm.spec=unlist(as.numeric(norm.spec))
  quant.mat=cbind(norm.other=quantile(norm.other,seq(0,1,by=0.05)),norm.spec=quantile(norm.spec,seq(0,1,by=0.05)))
 return(quant.mat)
 }
```

Here we compare quantiles and plot data:

Thyroid:
```{r}
compare.distribution(tissuename = "Thyroid",lfsr = lfsr,curvedata = log(exp.sort),thresh = 0.05 )
  
plot_tissuespecifictwo(tissuename = "Thyroid",lfsr = lfsr,curvedata = log(exp.sort),title = "Test",thresh = 0.05 )
```

Testis:



```{r}
compare.distribution(tissuename = "Testis",lfsr = lfsr,curvedata = log(exp.sort),thresh = 0.05)

plot_tissuespecifictwo(tissuename = "Testis",lfsr = lfsr,curvedata = log(exp.sort),title = "Test",thresh = 0.05 )
```

Whole Blood

```{r}
compare.distribution(tissuename = "Whole_Blood",lfsr = lfsr,curvedata = log(exp.sort),thresh = 0.05 )

plot_tissuespecifictwo(tissuename = "Whole_Blood",lfsr = lfsr,curvedata = log(exp.sort),title = "Test",thresh = 0.05)
```

Muscle_Skeletal
```{r}
compare.distribution(tissuename = "Muscle_Skeletal",lfsr = lfsr,curvedata = log(exp.sort),thresh = 0.05 )

plot_tissuespecifictwo(tissuename = "Muscle_Skeletal",lfsr = lfsr,curvedata = log(exp.sort),title = "Test",thresh = 0.05 )
```

```{r}

bar_example=function(gene.name,expr.sort)
  {
  index=which(rownames(expr.sort)==gene.name)
  barplot(as.matrix(expr.sort[index,]),las=2,main=gene.name,cex.names=0.5)
  }
```

Check testis: 
```{r}
library('qtlcharts')
plot_tissuespecific("Testis",lfsr,log(exp.sort),"log(exp.sort)",thresh=0.05,subset=1:44)
```

Show that they are eQTL:
```{r}
library('qtlcharts')
plot_tissuespecific("Testis",lfsr,pmash,"eQTLEffect",thresh=0.05,subset=1:44)
```

Check Whole Blood
```{r}
library('qtlcharts')
plot_tissuespecific("Whole_Blood",lfsr,log(exp.sort),"log(exp.sort)",thresh=0.05,subset=1:44)
```


QTLplot
```{r}
plot_tissuespecific("Whole_Blood",lfsr,pmash,"eQTLEffect",thresh=0.05,subset=1:44)
```

Check Thyroid
```{r}
library('qtlcharts')
plot_tissuespecific("Thyroid",lfsr,log(exp.sort),"log(exp.sort)",thresh=0.05,subset=1:44)
```


QTLplot
```{r}
plot_tissuespecific("Thyroid",lfsr,pmash,"eQTLEffect",thresh=0.05,subset=1:44)
```


Check Transformed Fibroblasts
```{r}
library('qtlcharts')
plot_tissuespecific("Cells_Transformed_fibroblasts",lfsr,log(exp.sort),"log(exp.sort)",thresh=0.05,subset=1:44)
```


QTLplot
```{r}
plot_tissuespecific("Cells_Transformed_fibroblasts",lfsr,pmash,"eQTLEffect",thresh=0.05,subset=1:44)
```

Check Muscle_Skeletal
```{r}
library('qtlcharts')
plot_tissuespecific("Muscle_Skeletal",lfsr,log(exp.sort),"log(exp.sort)",thresh=0.05,subset=1:44)
```


QTLplot
```{r}
plot_tissuespecific("Muscle_Skeletal",lfsr,pmash,"eQTLEffect",thresh=0.05,subset=1:44)
```

I am not seeing evidence of tissue specific expression.

##Check for our select examples:

These examples were quantitatively specific in WB:
```{r, whole.blood,cache=T}

gene.name="ENSG00000120029.8"
bar_example(gene.name,log(expr.sort))
```

and Qualitatively specific in Whole Blood:

```{r qualspecificwb, cache=T}
gene.name="ENSG00000078114.14"
bar_example(gene.name,log(expr.sort))
```

Testis qualitative:


```{r testis,cache=T}

gene.name="ENSG00000059588.5"
bar_example(gene.name,log(expr.sort))
```

So tissue-specificitiy in expression is the exception not the rule, and our examples are good.


