---
title: "Pairwise sharing by sign of eQTLs among tissues"
author: "Sarah Urbut"
output: workflowr::wflow_html
---

The plot generated here summarizes eQTL sharing by sign between all
pairs of tissues. Compare against Supplementary Figure 4 of the paper.

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, fig.width = 8,
                      fig.height = 4,fig.align = "center",
		      comment = "#")
```

## Set up environment

First, we load the lattice package used for generating the plot below.

```{r load-pkgs, message = FALSE}
library(lattice)
```

## Load data and MASH results

In the next code chunk, we load some GTEx summary statistics, as well
as some of the results generated from the MASH analysis of the GTEx
data.

```{r load-results}
out      <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")
maxb     <- out$test.b
maxz     <- out$test.z
out      <-readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                         "lite.single.expanded.V1.posterior.rds",sep = "."))
pm.mash  <- out$posterior.means
lfsr.all <- out$lfsr
standard.error <- maxb/maxz
pm.mash.beta <- pm.mash*standard.error
```

## Compute sharing-by-sign statistics

For each pair of tissues, compute the estimated proportion of eQTLs
that have effect sizes that are the same sign.

```{r generate-matrix}
thresh=0.05
pm.mash.beta=pm.mash.beta[rowSums(lfsr.all<0.05)>0,]
lfsr.mash=lfsr.all[rowSums(lfsr.all<0.05)>0,]
shared.fold.size=matrix(NA,nrow = ncol(lfsr.mash),ncol=ncol(lfsr.mash))
colnames(shared.fold.size)=rownames(shared.fold.size)=colnames(maxz)
for(i in 1:ncol(lfsr.mash)){
  for(j in 1:ncol(lfsr.mash)){
    sig.row=which(lfsr.mash[,i]<thresh)
    sig.col=which(lfsr.mash[,j]<thresh)
    a=(union(sig.row,sig.col))
    quotient=(pm.mash.beta[a,i]/pm.mash.beta[a,j])
    shared.fold.size[i,j]=mean(quotient > 0)
  }
}
```

## Plot heatmap of sharing by sign

Generate the heatmap using the "levelplot" function from the lattice
package.

```{r heatmap-sharing-sign, fig.height=10, fig.width=10}
all.tissue.order = read.table("../output/alltissueorder.txt")[,1]
clrs <- colorRampPalette(rev(c("#D73027","#FC8D59","#FEE090","#FFFFBF",
                               "#E0F3F8","#91BFDB","#4575B4")))(64)
lat=shared.fold.size[rev(all.tissue.order),rev(all.tissue.order)]
lat[lower.tri(lat)] <- NA
n=nrow(lat)
print(levelplot(lat[n:1,],col.regions = clrs,xlab = "",ylab = "",
      colorkey = TRUE))
```


