---
title: "Second covariance component "
author: "Sarah Urbut"
output: workflowr::wflow_html
---

---
title: "StructureEigenUk2"
output: html_document
---

Here we plot the correlation matrix for the second covariance
component. Its mixture weight isn't quite as high as the [dominant
covariance matrix](Fig.Uk3.html), but still quite strong.

The plots generated in the code below should be the same or very
similar to the top-left panel of Supplementary Figure 2.

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, fig.width = 8,
                      fig.height = 4,fig.align = "center")
```

## Set up environment

First, we load a few packages used in the code chunks below.

```{r load-pkgs, message = FALSE}
library(lattice)
library(ggplot2)
library(colorRamps)
```

## Load data and MASH results

In the next code chunk, we load some GTEx summary statistics, as well
as some of the results generated from the MASH analysis of the GTEx
data.

```{r load-results, echo = TRUE}
covmat <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                        "lite.single.expanded.rds",sep = "."))
pis    <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                        "lite.single.expanded.V1.pihat.rds",sep = "."))$pihat
z.stat <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")$test.z
pi.mat <- matrix(pis[-length(pis)],ncol = 54,nrow = 22,byrow = TRUE)
names  <- colnames(z.stat)
```

Next, we load the tissue indices:

```{r load-tissues-names}
h <- read.table("../output/uk2rowIndices.txt")[,1]
```

```{r corplotuk2,fig.height=10,fig.width=10}
k=2
colSums(pi.mat)[k]
x           <- cov2cor(covmat[[k]])
x[x < 0]    <- 0
colnames(x) <- names
rownames(x) <- names
```

Here we make the lattice plot:

```{r heatmapuk2final,fig.height=10,fig.width=10}
clrs <- colorRampPalette(rev(c("#D73027","#FC8D59","#FEE090","#FFFFBF",
                               "#E0F3F8","#91BFDB","#4575B4")))(64)
lat=x[rev(h),rev(h)]
lat[lower.tri(lat)] <- NA
n = nrow(lat)
print(levelplot(lat[n:1,],col.regions = clrs,xlab = "",ylab = "",
      colorkey = TRUE))
```

And the eigenvectors:

```{r eigenplots2}
missing.tissues=c(7,8,19,20,24,25,31,34,37)
color.gtex =read.table("../data/GTExColors.txt",sep = '\t',
             comment.char = '')[-missing.tissues,]
col = as.character(color.gtex[,2])
for(g in 1:3){
v=svd(covmat[[k]])$v[h,];d=svd(covmat[[k]])$d
par(mar=c(8,4.1,4.1,2.1))
barplot(v[,g]/v[which.max(abs(v[,g])),g],las=2,
        main=paste("Eigenvector",g,"of Uk",k),
        cex.names = 0.5,col=col[h],names=names[h])
}
````
