---
title: "Please add a more descriptive title"
author: "Sarah Urbut"
date: 2017-05-30
output: html_document
---

In this notebook, we make the metaplots comparing the original effect
estimates (*effects of what?*), and the posterior estimates obtained using 
the multivariate adaptive shrinkage model. *What is the main result(s) we 
are showing in this notebook? What is the point of showing these plots.* 
The plots below were used to create Fig. 4 of the paper.

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE,comment = "#",fig.width = 8,
                      fig.height = 4,fig.align = "center")
```

## Set up environment

First, we load the rmeta package, as well as some functions defined
for MASH analyses.

```{r load-pkgs, message = FALSE}
source("../workflow/normfuncs.R")
library(rmeta)
```

## Load data and MASH results

*Please explain here what this next code chunk does. It looks like it is
reading a bunch of data files. What data are being loaded?*

```{r load-data}
b.stat <- read
z.stat <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")$test.z
standard.error <- b.stat/z.stat
covmat <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                        "lite.single.expanded.rds",sep = "."))
b.stat          <- read.table("../output/maxbetahats.txt")
posterior.means <- read.table("../output/withvhatposterior.means.txt")[,-1]
lfsr            <- read.table("../output/withvhatlfsr.txt")[,-1]
mar.var         <- read.table("../output/withvhatmarginal.var.txt")[,-1]
colnames(lfsr)  <-
  colnames(mar.var) <- 
  colnames(posterior.means) <- 
  colnames(z.stat)
posterior.betas <- standard.error * posterior.means
pm.beta.norm    <- het.norm(posterior.betas)
```

Load the tissue indices:

```{r load-tissues-names}
missing.tissues <- c(7,8,19,20,24,25,31,34,37)
uk3labels       <- read.table("../Data/uk3rowindices.txt")[,1]
```

*In this next chunk you are defining a function. Can you briefly explain
in 1-2 sentences what this function does, and how you will use it in the code
chunks below?*

```{r define-create-metaplot-function}
create.metaplot <- function (j) {
  gtex.colors <- read.table('../Data/GTExColors.txt', sep = '\t', 
                            comment.char = '')[-missing.tissues,2]
  gtex.colors <- gtex.colors[uk3labels]

  pm.beta.norm  <- pm.beta.norm[,uk3labels] # Shuffle columns.
  z.shuffle     <- z.stat[,uk3labels]
  b.shuffle     <- b.stat[,uk3labels]
  post.var      <- mar.var[uk3labels]
  post.bshuffle <- posterior.betas[,uk3labels]
  sem.shuffle   <- standard.error[,uk3labels]
  lfsr          <- lfsr[,uk3labels]
  plot.title    <- strsplit(rownames(z.stat)[j], "[.]")[[1]][1]

  x <- as.numeric(post.bshuffle[j,])

  layout(t(1:2))
  
  metaplot(as.numeric(b.shuffle[j,]),as.numeric(sem.shuffle[j,]),xlab = "",
           ylab = "",colors = meta.colors(box = as.character(gtex.colors)),
           xlim = c(-1,1))
  title(plot.title)

  # Transform to posterior sd of beta.
  sd <- as.numeric(sem.shuffle[j,]) * sqrt(as.numeric(post.var[j,]))
  metaplot(x,sd,xlab = "",ylab = "",
           colors = meta.colors(box = as.character(gtex.colors)),
           xlim = c(-1,1))
  title(plot.title)
}
```

## *MCPH1* gene 

Our first example compares the *MCPH1* original eQTL estimates against 
the posterior estimates.

*What are the two plots showing? What is interesting about this example?
What is the take-home message from this plot?*

*Please add labels to the horizontal and vertical axes. Which of these 
plots shows the original effect estimates, and which shows the posterior 
("shrunk") estimates?*

```{r metaplot_MCPH1, fig.keep = "last"}
three.ex.3 <- 
  which(rownames(z.stat) == "ENSG00000249898.3_8_6521432_T_C_b37")
newfunc.2(three.ex.3)

# This line of code doesn't seem to do anything. Why is it included?
whole.blood.spec <-  
  which(rowSums(pm.beta.norm[,-44]<0.5)==43&(rowSums(lfsr[,1:44]<0.05)>=40))
```

## *FLJ13114* gene

*What is interesting about this example?
What is the take-home message from this plot?*

```{r metaplot_FLJ13114}
five.ex <- which(rownames(z.stat) == "ENSG00000120029.8_10_103924251_G_A_b37")

# This line of code doesn't seem to do anything. Why is it included?
testes.spec <-  which(rowSums(pm.beta.norm[,-40]<0.5) == 43 &
                    (rowSums(lfsr[,1:44]<0.05)>=40))[1:10]

newfunc.2(five.ex)
```
 
## *RALBP1* gene

*What is interesting about this example?
What is the take-home message from this plot?*

```{r metaplot_RALBP1}
wholebloodfour <- 
  (which(rownames(z.stat) == "ENSG00000017797.7_18_9488704_C_T_b37"))
newfunc.2(wholebloodfour)
```
