---
title: "Correlation patterns from eighth covariance component"
author: "Sarah Urbut"
output: workflowr::wflow_html
---

Here we plot the correlation matrix for the eighth covariance
component, which captures testis-specific effects.

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, fig.width = 8,
                      fig.height = 4,fig.align = "center",
                      comment = "#")
```

## Set up environment

First, we load a couple plotting packages used in the code chunks below.

```{r load-pkgs, message = FALSE}
library(lattice)
library(colorRamps)
```

## Load data and MASH results

In the next code chunk, we load some GTEx summary statistics, as well
as some of the results generated from the MASH analysis of the GTEx
data.

```{r load-results}
covmat <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                        "lite.single.expanded.rds",sep = "."))
pis    <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                        "lite.single.expanded.V1.pihat.rds",sep = "."))$pihat
z.stat <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")$test.z
pi.mat <- matrix(pis[-length(pis)],ncol = 54,nrow = 22,byrow = TRUE)
names  <- colnames(z.stat)
```

Next, we load the tissue indices:

```{r load-tissues-names}
h <- read.table("../output/uk8rowIndices.txt")[,1]
```

For the plots of the eigenvectors, we load the colours that are
conventionally used to represent the tissues in plots.

```{r load-tissue-colors}
missing.tissues <- c(7,8,19,20,24,25,31,34,37)
color.gtex      <- read.table("../data/GTExColors.txt",sep = '\t',
                              comment.char = '')[-missing.tissues,]
```

Compute the correlations from the $k=8$ covariance matrix.

```{r get-correlations}
k           <- 8
x           <- cov2cor(covmat[[k]])
x[x<0]      <- 0
colnames(x) <- names
rownames(x) <- names
```

## Generate heatmap of Uk8 covariance matrix

Now we produce the heatmap showing the full covariance matrix.

```{r heatmapuk8final, fig.height=10, fig.width=10}
clrs <- colorRampPalette(rev(c("#D73027","#FC8D59","#FEE090","#FFFFBF",
                               "#E0F3F8","#91BFDB","#4575B4")))(64)
lat=x[rev(h),rev(h)]
lat[lower.tri(lat)] <- NA
n=nrow(lat)
print(levelplot(lat[n:1,],col.regions = clrs,xlab = "",ylab = "",
      colorkey = TRUE))
```

## Plot eigenvector capturing the predominant pattern

The top eigenvector captures the predominant pattern in the Uk8
covariance matrix.

```{r plot-eigenvectors, fig.width = 6, fig.height = 4}
col = as.character(color.gtex[,2])
k=8
g=1
v=svd(covmat[[k]])$v[h,]
rownames(v)=colnames(v)=names[h]
par(mar=c(8,4.1,4.1,2.1))
barplot(v[,g]/v[which.max(abs(v[,g])),g],las=2,
        main=paste("Eigenvector",g,"of Uk",k),
        cex.names = 0.5,col=col[h],names=names[h])
````
