---
title: "Please add a more descriptive title"
author: "Sarah Urbut"
date: 2017-05-30
output: html_document
---

In this notebook, we make the metaplots comparing the original effect
estimates (*effects of what?*), and the posterior estimates obtained using 
the multivariate adaptive shrinkage model. *What is the main result(s) we 
are showing in this notebook? What is the point of showing these plots.* 
The plots below were used to create Fig. 4 of the paper.

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE,comment = "#",fig.width = 8,
                      fig.height = 4,fig.align = "center")
```

## Set up environment

First, we load the rmeta package, as well as some functions defined
for MASH analyses.

```{r load-pkgs, message = FALSE}
source("../workflows/normfuncs.R")
library(rmeta)
```

## Load data and MASH results

In the next code chunk, we load some GTEx summary statistics, as well
as some of the results generated from the MASH analysis of the GTEx
data.

```{r load-results}
out <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                     "lite.single.expanded.V1.posterior.rds",sep = "."))
b.stat <- read.table("../output/maxbetahats.txt")
z.stat <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")$test.z
covmat <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                        "lite.single.expanded.rds",sep = "."))
posterior.means <- out$posterior.means
lfsr            <- out$lfsr
mar.var         <- out$marginal.var
rm(out)
colnames(lfsr)  <-
  colnames(mar.var) <- 
  colnames(posterior.means) <- 
  colnames(z.stat)
standard.error  <- b.stat/z.stat
posterior.betas <- standard.error * posterior.means
pm.beta.norm    <- het.norm(posterior.betas)
```

Load the tissue indices:

```{r load-tissues-names}
missing.tissues <- c(7,8,19,20,24,25,31,34,37)
uk3labels       <- read.table("../output/uk3rowindices.txt")[,1]
```

For the plots of the eigenvectors, we load the colours that are
conventionally used to represent the tissues in plots.

```{r load-tissue-colors}
gtex.colors <- read.table('../data/GTExColors.txt', sep = '\t', 
                          comment.char = '')[-missing.tissues,2]
gtex.colors <- gtex.colors[uk3labels]
```

## *MCPH1* gene 

Our first example compares the *MCPH1* original eQTL estimates against 
the posterior estimates.

```{r define-create-metaplot-function}
create.metaplot <- function (j) {

  pm.beta.norm  <- pm.beta.norm[,uk3labels] # Shuffle columns.
  z.shuffle     <- z.stat[,uk3labels]
  b.shuffle     <- b.stat[,uk3labels]
  post.var      <- mar.var[,uk3labels]
  post.bshuffle <- posterior.betas[,uk3labels]
  sem.shuffle   <- standard.error[,uk3labels]
  lfsr          <- lfsr[,uk3labels]
  plot.title    <- strsplit(rownames(z.stat)[j], "[.]")[[1]][1]

  x <- as.numeric(post.bshuffle[j,])

  layout(t(1:2))
  
  metaplot(as.numeric(b.shuffle[j,]),as.numeric(sem.shuffle[j,]),xlab = "",
           ylab = "",colors = meta.colors(box = as.character(gtex.colors)),
           xlim = c(-1,1))
  title(plot.title)

  # Transform to posterior sd of beta.
  sd <- as.numeric(sem.shuffle[j,]) * sqrt(as.numeric(post.var[j,]))
  metaplot(x,sd,xlab = "",ylab = "",
           colors = meta.colors(box = as.character(gtex.colors)),
           xlim = c(-1,1))
  title(plot.title)
}
```

*What are the two plots showing? What is interesting about this example?
What is the take-home message from this plot?*

*Please add labels to the horizontal and vertical axes. Which of these 
plots shows the original effect estimates, and which shows the posterior 
("shrunk") estimates?*

```{r metaplot-MCPH1, fig.keep = "last"}
create.metaplot(which(rownames(z.stat) ==
  "ENSG00000249898.3_8_6521432_T_C_b37"))
```

## *FLJ13114* gene

*What is interesting about this example?
What is the take-home message from this plot?*

```{r metaplot-FLJ13114}
five.ex <- which(rownames(z.stat) == "ENSG00000120029.8_10_103924251_G_A_b37")

# This line of code doesn't seem to do anything. Why is it included?
testes.spec <-  which(rowSums(pm.beta.norm[,-40]<0.5) == 43 &
                    (rowSums(lfsr[,1:44]<0.05)>=40))[1:10]

newfunc.2(five.ex)
```
 
## *RALBP1* gene

*What is interesting about this example?
What is the take-home message from this plot?*

```{r metaplot_RALBP1}
wholebloodfour <- 
  (which(rownames(z.stat) == "ENSG00000017797.7_18_9488704_C_T_b37"))
newfunc.2(wholebloodfour)
```
