---
title: "Correlation patterns from second covariance component"
author: "Sarah Urbut"
output: workflowr::wflow_html
---

Here we plot the correlation matrix for the second covariance
component. Its mixture weight isn't quite as high as the [dominant
covariance matrix](Fig.Uk3.html), but still one of the more
predominant components.

The plots generated in the code below should be the same or very
similar to the top-left panel of Supplementary Figure 2.

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, fig.width = 8,
                      fig.height = 4,fig.align = "center")
```

## Set up environment

First, we load a couple plotting packages used in the code chunks below.

```{r load-pkgs, message = FALSE}
library(lattice)
library(colorRamps)
```

## Load data and MASH results

In the next code chunk, we load some GTEx summary statistics, as well
as some of the results generated from the MASH analysis of the GTEx
data.

```{r load-results}
covmat <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                        "lite.single.expanded.rds",sep = "."))
pis    <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                        "lite.single.expanded.V1.pihat.rds",sep = "."))$pihat
z.stat <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")$test.z
pi.mat <- matrix(pis[-length(pis)],ncol = 54,nrow = 22,byrow = TRUE)
names  <- colnames(z.stat)
```

Next, we load the tissue indices:

```{r load-tissues-names}
h <- read.table("../output/uk2rowIndices.txt")[,1]
```

For the plots of the eigenvectors, we load the colours that are
conventionally used to represent the tissues in plots.

```{r load-tissue-colors}
missing.tissues <- c(7,8,19,20,24,25,31,34,37)
color.gtex      <- read.table("../data/GTExColors.txt",sep = '\t',
                              comment.char = '')[-missing.tissues,]
```

Compute the correlations from the $k=2$ covariance matrix.

```{r get-correlations}
k           <- 2
x           <- cov2cor(covmat[[k]])
x[x < 0]    <- 0
colnames(x) <- names
rownames(x) <- names
```

## Generate heatmap of Uk2 covariance matrix

Now we produce the heatmap showing the full covariance matrix.

```{r heatmapuk2final,fig.height=10,fig.width=10}
clrs <- colorRampPalette(rev(c("#D73027","#FC8D59","#FEE090","#FFFFBF",
                               "#E0F3F8","#91BFDB","#4575B4")))(64)
lat=x[rev(h),rev(h)]
lat[lower.tri(lat)] <- NA
n = nrow(lat)
print(levelplot(lat[n:1,],col.regions = clrs,xlab = "",ylab = "",
      colorkey = TRUE))
```

## Plot eigenvectors capturing predominant patterns

The eigenvectors capture the predominant patterns in the Uk3
covariance matrix.

```{r plot-eigenvectors, fig.width = 6, fig.height = 4}
col = as.character(color.gtex[,2])
for(g in 1:3){
  v=svd(covmat[[k]])$v[h,];d=svd(covmat[[k]])$d
  par(mar=c(8,4.1,4.1,2.1))
  barplot(v[,g]/v[which.max(abs(v[,g])),g],las=2,
          main=paste("Eigenvector",g,"of Uk",k),
          cex.names = 0.5,col=col[h],names=names[h])
}
```
