---
title: "Examples illustrating how mash uses patterns of sharing to inform effect estimates"
author: "Sarah Urbut"
output: workflowr::wflow_html
---

Having estimated patterns of sharing from the data, mash exploits
these patterns to improve effect estimates at each putative eQTL. Here
we give three examples can provide intuition into the way that mash
achieves improved accuracy of effect estimation.

Compare the plots against Figure 4 of the paper.

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE,comment = "#",fig.width = 8,
                      fig.height = 4,fig.align = "center")
```

## Set up environment

First, we load the rmeta package, as well as some functions defined
for MASH analyses.

```{r load-pkgs, message = FALSE}
source("../workflows/normfuncs.R")
library(rmeta)
```

## Load data and MASH results

In the next code chunk, we load some GTEx summary statistics, as well
as some of the results generated from the MASH analysis of the GTEx
data.

```{r load-results}
out    <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")
b.stat <- out$test.b
z.stat <- out$test.z
out    <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                        "lite.single.expanded.V1.posterior.rds",sep = "."))
posterior.means <- out$posterior.means
lfsr            <- out$lfsr
mar.var         <- out$marginal.var
rm(out)
colnames(lfsr)  <-
  colnames(mar.var) <- 
  colnames(posterior.means) <- 
  colnames(z.stat)
standard.error  <- b.stat/z.stat
posterior.betas <- standard.error * posterior.means
pm.beta.norm    <- het.norm(posterior.betas)
```

Load the tissue indices:

```{r load-tissues-names}
missing.tissues <- c(7,8,19,20,24,25,31,34,37)
uk3labels       <- read.table("../output/uk3rowindices.txt")[,1]
```

For the plots of the eigenvectors, we load the colours that are
conventionally used to represent the tissues in plots.

```{r load-tissue-colors}
gtex.colors <- read.table('../data/GTExColors.txt', sep = '\t', 
                          comment.char = '')[-missing.tissues,2]
gtex.colors <- gtex.colors[uk3labels]
```

## *MCPH1* gene 

In the first example, the vast majority of effect estimates are
positive in each tissue, with the strongest signals in a subset of
brain tissues. Based on the patterns of sharing learned in the first
step, mash estimates the effects in all tissues to be positive---even
those with negative observed effects. This is because the few modest
negative effects at this eQTL are outweighed by the strong background
information that effects are highly correlated among tissues.

To create the metaplot, we first define a function which we will use
in this example, and reuse in subsequent examples.

```{r define-create-metaplot-function}
create.metaplot <- function (j) {

  pm.beta.norm  <- pm.beta.norm[,uk3labels] # Shuffle columns.
  z.shuffle     <- z.stat[,uk3labels]
  b.shuffle     <- b.stat[,uk3labels]
  post.var      <- mar.var[,uk3labels]
  post.bshuffle <- posterior.betas[,uk3labels]
  sem.shuffle   <- standard.error[,uk3labels]
  lfsr          <- lfsr[,uk3labels]
  plot.title    <- strsplit(rownames(z.stat)[j], "[.]")[[1]][1]

  x <- as.numeric(post.bshuffle[j,])

  layout(t(1:2))
  
  metaplot(as.numeric(b.shuffle[j,]),as.numeric(sem.shuffle[j,]),xlab = "",
           ylab = "",colors = meta.colors(box = as.character(gtex.colors)),
           xlim = c(-1,1))
  title(plot.title)

  # Transform to posterior sd of beta.
  sd <- as.numeric(sem.shuffle[j,]) * sqrt(as.numeric(post.var[j,]))
  metaplot(x,sd,xlab = "",ylab = "",
           colors = meta.colors(box = as.character(gtex.colors)),
           xlim = c(-1,1))
  title(plot.title)
}
```

Now create the *MCHP1* metaplot summarizing the eQTL effect
estimates. The original effect estimates are shown on the left-hand
side, and the shrunken estimates from mash are shown on the right-hand
side.

```{r metaplot-MCPH1, fig.keep = "last"}
create.metaplot(which(rownames(z.stat) ==
  "ENSG00000249898.3_8_6521432_T_C_b37"))
```

## *FLJ13114* gene

In the second example, the effect estimates in non-brain tissues are
mostly positive, but modest in size, and only one effect is,
individually, nominally significant. However, combining information
among tissues, mash effect estimates in non-brain tissues are all
positive, and mostly "significant".

```{r metaplot-FLJ13114}
create.metaplot(which(rownames(z.stat) ==
  "ENSG00000120029.8_10_103924251_G_A_b37"))
```
 
## *RALBP1* gene

In this example, the effect estimates vary in sign, and are modest
except for a very strong signal in whole blood. While
whole-blood-specific effects are estimated to be rare, mash recognizes
that the strong data at this eQTL outweigh this background
information, and estimates a strong effect in blood with insignificant
effects in other tissues.

```{r metaplot-RALBP1}
create.metaplot(which(rownames(z.stat) ==
  "ENSG00000017797.7_18_9488704_C_T_b37"))
```
