---
title: "Overall sharing among top eQTLs"
author: "Sarah Urbut, Gao Wang, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

Here we summarize overall sharing of effects by sign and by
magnitude. Compare the table at the bottom of this page against Table
2 in the manuscript.

Because a major feature of these data is that brain tissues generally
show more similar effects than non-brain tissues, we also compute
results separately from subsets of brain and non-brain tissues.

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, fig.width = 8,
                      fig.height = 6,fig.align = "center",
                      comment = "#")
```

## Set up environment

First, we load some functions defined for mash analyses.

```{r load-functions}
source("../code/normfuncs.R")
```
This is the threshold used to determine which genes have at least one
significant effect across tissues.

```{r thresh}
thresh <- 0.05
```

## Load data and mash results

Load some GTEx summary statistics, as well as some of the results
generated from the mash analysis of the GTEx data.

```{r load-results}
out            <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")
maxbeta        <- out$strong.b
maxz           <- out$strong.z
standard.error <- out$strong.s
out  <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                      "lite.single.expanded.V1.posterior.rds",sep = "."))
pm.mash        <- out$posterior.means
pm.mash.beta   <- pm.mash*standard.error
lfsr           <- out$lfsr
lfsr[lfsr < 0] <- 0
tissue.names   <- as.character(read.table("../data/abbreviate.names.txt")[,2])
colnames(lfsr) <- tissue.names
```

Load the results generated from the mash analysis of the GTEx data
after removing the data from the brain tissues.

```{r load-without-brain-results} 
lfsr.nobrain           <- read.table("../output/nobrainlfsr.txt")[,-1]
colnames(lfsr.nobrain) <- tissue.names[-c(7:16)]
pm.mash.nobrain <-
  as.matrix(read.table("../output/nobrainposterior.means.txt")[,-1]) *
    standard.error[,-c(7:16)]
```

Load the results generated from the mash analysis of the GTEx data for
the brain tissues only.

```{r load-brain-only-results}
lfsr.brain.only           <- read.table("../output/brainonlylfsr.txt")[,-1]
colnames(lfsr.brain.only) <- tissue.names[c(7:16)]
pm.mash.brain.only <-
  as.matrix(read.table("../output/brainonlyposterior.means.txt")[,-1]) *
    standard.error[,c(7:16)]
```

## Compute overall sharing by sign and magnitude

Compute the amount of eQTL sharing by sign, in all tissues, and
separately in brain and non-brain tissues. "Sharing by" sign requires
that the effect has the same sign as the strongest effect among
tissues.

```{r compute-heterogeneity-by-sign}
sigmat  <- (lfsr<=thresh)
nsig    <-  rowSums(sigmat)
signall <- mean(het.norm(pm.mash.beta[nsig>0,])>0)

sigmat          <- (lfsr[,-c(7:16)]<=thresh)
nsig            <-  rowSums(sigmat)
signall.nobrain <- mean(het.norm(pm.mash.beta[nsig,-c(7:16)])>0)

sigmat            <- (lfsr[,c(7:16)]<=thresh)
nsig              <- rowSums(sigmat)
signall.brainonly <- mean(het.norm(pm.mash.beta[nsig>0,c(7:16)])>0)

sigmat      <- (lfsr.nobrain<=thresh)
nsig        <- rowSums(sigmat)
signnobrain <- mean(het.norm(pm.mash.nobrain[nsig>0,])>0)

sigmat        <- (lfsr.brain.only<=thresh)
nsig          <- rowSums(sigmat)
signbrainonly <- mean(het.norm(pm.mash.brain.only[nsig>0,])>0)
```

Compute the amount of sharing by magnitude, in all tissues, and
separately in brain and non-brain tissues. "Sharing by Magnitude"
requires that the effect is also within a factor of 2 of the strongest
effect.

```{r compute-heterogeneity-by-magnitude}
sigmat <- (lfsr<=thresh)
nsig   <- rowSums(sigmat)
magall <- mean(het.norm(pm.mash.beta[nsig>0,])>0.5)

sigmat <- (lfsr[,-c(7:16)]<=thresh)
nsig   <- rowSums(sigmat)
magall.excludingbrain <- mean(het.norm(pm.mash.beta[nsig>0,-c(7:16)]) > 0.5)

sigmat <- (lfsr[,c(7:16)]<=thresh)
nsig   <- rowSums(sigmat)
magall.brainonly <- mean(het.norm(pm.mash.beta[nsig>0,c(7:16)]) > 0.5)

sigmat     <- (lfsr.nobrain<=thresh)
nsig       <- rowSums(sigmat)
magnobrain <- mean(het.norm(pm.mash.nobrain[nsig>0,]) > 0.5)

sigmat   <- (lfsr.brain.only<=thresh)
nsig     <- rowSums(sigmat)
magbrain <- mean(het.norm(pm.mash.brain.only[nsig>0,]) > 0.5)
```

Summarize these calculations in a single table. The numbers in
parentheses are obtained by the secondary mash analyses on the
brain-only and non-brain tissue subsets.

```{r sharing-summary}
round(matrix(rbind(c(signall,signall.nobrain,signnobrain,
               signall.brainonly,signbrainonly),
             c(magall,magall.excludingbrain,magnobrain,
			   magall.brainonly,magbrain)),
         nrow = 2,ncol = 5,
         dimnames = list(c("shared by sign","shared by magnitude"),
                    	 c("all tissues","non-brain","(non-brain)",
	                       "brain","(brain)"))),
	  digits = 3)
```

The results confirm extensive eQTL sharing among tissues, particularly
among the brain tissues; sharing in sign exceeds 85% in all cases, and
is as high as 96% among the brain tissues.

Sharing in magnitude is inevitably lower, because sharing in magnitude
implies sharing in sign. Overall, on average 36% of tissues show an
effect within a factor of 2 of the strongest effect at each top
eQTL.

However, within brain tissues this number increases to 76%. That is,
not only do eQTLs tend to be shared among the brain tissues, but the
effect sizes tend to be quite homogeneous.
