---
title: "heterogeneitytablesimulation"
output: pdf_document
---

```{r setup}
library('knitr')
knitr::opts_chunk$set(eval = FALSE)
source("../../Scripts/normfuncs.R")
```

##Heterogeneity Analysis: Shared Structured, Sharing by sign

```{r ,echo=T}

data=readRDS("../../../Dropbox/formatthew/simdata.rds")
t=data$tstat;bhat=data$betahat;sebetahat=data$sebetahat;beta=data$beta;v.j=matrix(rep(1,ncol(t)*nrow(t)),ncol=ncol(t),nrow=nrow(t))

mash.means=read.table("../../../Dropbox/formatthew/shared/sharedashcutoffomega2jun15posterior.means.txt")[,-1]

bma.means=read.table("../../../Dropbox/formatthew/shared/noashsharedwithzerobmaallposterior.means.txt")[,-1]

ash.means=read.table("../../../Dropbox/formatthew/shared/univariate.ash.pm.txt")


lfsr.mash=read.table("../../../Dropbox/formatthew/shared/sharedashcutoffomega2jun15lfsr.txt")[,-1]
lfsr.bma=read.table("../../../Dropbox/formatthew/shared/noashsharedwithzerobmaalllfsr.txt")[,-1]
lfsr.ash=read.table("../../../Dropbox/formatthew/shared/univariate.ash.lfsr.txt")



standard.error=data$sebetahat[1:20000,]

pm.mash.beta=mash.means*standard.error
pm.bma.beta=bma.means*standard.error
pm.ash.beta=ash.means*standard.error

thresh=0.05
```

Here, we show the Proportion of Sharing by Sign:

```{r tables}

sigmat=(lfsr.mash<=thresh)
nsig= rowSums(sigmat)
#(signall=mean(het.norm(pm.mash.beta[nsig>0,])>0))
(signall.mash=mean(het.norm(pm.mash.beta[1:400,])>0))

##BMA
sigmat=(lfsr.bma<=thresh)
nsig= rowSums(sigmat)
#(signall=mean(het.norm(pm.bma.beta[nsig>0,])>0))
(signall.bma=mean(het.norm(pm.bma.beta[1:400,])>0))


##ASH
sigmat=(lfsr.ash<thresh)
nsig= rowSums(sigmat)
#(signall=mean(het.norm(pm.ash.beta[nsig>0,])>0))
(signall.ash=mean(het.norm(pm.ash.beta[1:400,])>0))
####SHow that results are robust in specific analysis

(truth=(mean(het.norm(data$beta[1:400,])>0)))
(standard=mean(het.norm(data$betahat[1:400,])>0))



(RMLE=sqrt(mean((standard-truth)^2)))
#RMLE=1
(RRMSE.mash=sqrt(mean((signall.mash-truth)^2))/RMLE)
(RRMSE.bma=sqrt(mean((signall.bma-truth)^2))/RMLE)
(RRMSE.ash=sqrt(mean((signall.ash-truth)^2))/RMLE)

rmse.all.table=cbind(mash=RRMSE.mash,bmalite=RRMSE.bma,ash=RRMSE.ash)
barplot(as.numeric(rmse.all.table),main="Shared, Structured Effects: Sign heterogeneity",
        ylab="relative error (RRMSE)",xlab="Method",col=c("green","blue","red"),names=colnames(rmse.all.table),ylim=c(0,1.5),cex.main=1.5,cex.lab=1,cex.names=1,las=1)
```

##Heterogeneity Analysis: Independent SSimulation by Sign

```{r ,echo=T}

data=readRDS("../../../Dropbox/formatthew/independentsim.rds")
t=data$tstat;bhat=data$betahat;sebetahat=data$sebetahat;beta=data$beta;v.j=matrix(rep(1,ncol(t)*nrow(t)),ncol=ncol(t),nrow=nrow(t))


mash.means=read.table("../../../Dropbox/formatthew/independentsim_all/independentsimashcutoffomega2jun15posterior.means.txt")[,-1]
ash.means=read.table("../../../Dropbox/formatthew/independentsim_all/univariate.ash.pmind.txt")

bma.means=read.table("../../../Dropbox/formatthew/independentsim_all/noashindependentwithzerobmaallposterior.means.txt")[,-1]



lfsr.mash=read.table("../../../Dropbox/formatthew/independentsim_all/independentsimashcutoffomega2jun15lfsr.txt")[,-1]
lfsr.bma=read.table("../../../Dropbox/formatthew/independentsim_all/noashindependentwithzerobmaalllfsr.txt")[,-1]
lfsr.ash=read.table("../../../Dropbox/formatthew/independentsim_all/univariate.ashind.lfsr.txt")




standard.error=data$sebetahat[1:20000,]

pm.mash.beta=mash.means*standard.error
pm.bma.beta=bma.means*standard.error
pm.ash.beta=ash.means*standard.error

thresh=0.05
```

Here, we show the Proportion of Sharing by Sign:

```{r tables2}

sigmat=(lfsr.mash<=thresh)
nsig= rowSums(sigmat)
#(signall=mean(het.norm(pm.mash.beta[nsig>0,])>0))
(signall.mash=mean(het.norm(pm.mash.beta[1:400,])>0))

##BMA
sigmat=(lfsr.bma<=thresh)
nsig= rowSums(sigmat)
#(signall=mean(het.norm(pm.bma.beta[nsig>0,])>0))
(signall.bma=mean(het.norm(pm.bma.beta[1:400,])>0))


##ASH
sigmat=(lfsr.ash<thresh)
nsig= rowSums(sigmat)
#(signall=mean(het.norm(pm.ash.beta[nsig>0,])>0))
(signall.ash=mean(het.norm(pm.ash.beta[1:400,])>0))


(truth=(mean(het.norm(data$beta[1:400,])>0)))
(standard=mean(het.norm(data$betahat[1:400,])>0))


(RMLE=sqrt(mean((standard-truth)^2)))
(RRMSE.mash=sqrt(mean((signall.mash-truth)^2))/RMLE)

(RRMSE.bma=sqrt(mean((signall.bma-truth)^2))/RMLE)
(RRMSE.ash=sqrt(mean((signall.ash-truth)^2))/RMLE)



rmse.all.table=cbind(mash=RRMSE.mash,bmalite=RRMSE.bma,ash=RRMSE.ash)
barplot(as.numeric(rmse.all.table),main="Shared, Unstructured Effects: Sign heterogeneity",
        ylab="relative error (RRMSE)",xlab="Method",col=c("green","blue","red"),names=colnames(rmse.all.table),ylim=c(0,1.5),cex.main=1.5,cex.lab=1,cex.names=1,las=1)


```

##Heterogeneity Analysis: Shared,Structured by magnitude


```{r ld2,echo=T}

data=readRDS("../../../Dropbox/formatthew/simdata.rds")
t=data$tstat;bhat=data$betahat;sebetahat=data$sebetahat;beta=data$beta;v.j=matrix(rep(1,ncol(t)*nrow(t)),ncol=ncol(t),nrow=nrow(t))

mash.means=read.table("../../../Dropbox/formatthew/shared/sharedashcutoffomega2jun15posterior.means.txt")[,-1]
ash.means=read.table("../../../Dropbox/formatthew/shared/univariate.ash.pm.txt")
bma.means=read.table("../../../Dropbox/formatthew/shared/noashsharedwithzerobmaallposterior.means.txt")[,-1]



lfsr.mash=read.table("../../../Dropbox/formatthew/shared/sharedashcutoffomega2jun15lfsr.txt")[,-1]
lfsr.bma=read.table("../../../Dropbox/formatthew/shared/noashsharedwithzerobmaalllfsr.txt")[,-1]
lfsr.ash=read.table("../../../Dropbox/formatthew/shared/univariate.ash.lfsr.txt")



standard.error=data$sebetahat[1:20000,]

pm.mash.beta=mash.means*standard.error
pm.bma.beta=bma.means*standard.error
pm.ash.beta=ash.means*standard.error

thresh=0.05
```

Here, we show the Proportion of Sharing by Sign:

```{r tables3}

sigmat=(lfsr.mash<=thresh)
nsig= rowSums(sigmat)
(signall=mean(het.norm(pm.mash.beta[nsig>0,])>0.5))
(signall.mash=mean(het.norm(pm.mash.beta[1:400,])>0.5))

##BMA
sigmat=(lfsr.bma<=thresh)
nsig= rowSums(sigmat)
(signall=mean(het.norm(pm.bma.beta[nsig>0,])>0.5))
(signall.bma=mean(het.norm(pm.bma.beta[1:400,])>0.5))


##ASH
sigmat=(lfsr.ash<thresh)
nsig= rowSums(sigmat)
(signall=mean(het.norm(pm.ash.beta[nsig>0,])>0.5))
(signall.ash=mean(het.norm(pm.ash.beta[1:400,])>0.5))
####SHow that results are robust in specific analysis

(truth=(mean(het.norm(data$beta[1:400,])>0.5)))
(standard=mean(het.norm(data$betahat[1:400,])>0.5))


(RMLE=sqrt(mean((standard-truth)^2)))
(RRMSE.mash=sqrt(mean((signall.mash-truth)^2))/RMLE)
(RRMSE.bma=sqrt(mean((signall.bma-truth)^2))/RMLE)
(RRMSE.ash=sqrt(mean((signall.ash-truth)^2))/RMLE)



rmse.all.table=cbind(mash=RRMSE.mash,bmalite=RRMSE.bma,ash=RRMSE.ash)
barplot(as.numeric(rmse.all.table),main="Shared, Structured Effects: Magnitude heterogeneity",
        ylab="relative error (RRMSE)",xlab="Method",col=c("green","blue","red"),names=colnames(rmse.all.table),ylim=c(0,4.0),cex.main=1.5,cex.lab=1,cex.names=1,las=1)



```


##Heterogeneity Analysis: Independent by magnitude

```{r ld3,echo=T}

data=readRDS("../../../Dropbox/formatthew/independentsim.rds")
t=data$tstat;bhat=data$betahat;sebetahat=data$sebetahat;beta=data$beta;v.j=matrix(rep(1,ncol(t)*nrow(t)),ncol=ncol(t),nrow=nrow(t))


mash.means=read.table("../../../Dropbox/formatthew/independentsim_all/independentsimashcutoffomega2jun15posterior.means.txt")[,-1]
ash.means=read.table("../../../Dropbox/formatthew/independentsim_all/univariate.ash.pmind.txt")

bma.means=read.table("../../../Dropbox/formatthew/independentsim_all/noashindependentwithzerobmaallposterior.means.txt")[,-1]



lfsr.mash=read.table("../../../Dropbox/formatthew/independentsim_all/independentsimashcutoffomega2jun15lfsr.txt")[,-1]
lfsr.bma=read.table("../../../Dropbox/formatthew/independentsim_all/noashindependentwithzerobmaalllfsr.txt")[,-1]
lfsr.ash=read.table("../../../Dropbox/formatthew/independentsim_all/univariate.ashind.lfsr.txt")


standard.error=data$sebetahat[1:20000,]

pm.mash.beta=mash.means*standard.error
pm.bma.beta=bma.means*standard.error
pm.ash.beta=ash.means*standard.error

thresh=0.05
```

Here, we show the Proportion of Sharing by Sign:

```{r tables4}

sigmat=(lfsr.mash<=thresh)
nsig= rowSums(sigmat)
(signall=mean(het.norm(pm.mash.beta[nsig>0,])>0.5))
(signall.mash=mean(het.norm(pm.mash.beta[1:400,])>0.5))

##BMA
sigmat=(lfsr.bma<=thresh)
nsig= rowSums(sigmat)
(signall=mean(het.norm(pm.bma.beta[nsig>0,])>0.5))
(signall.bma=mean(het.norm(pm.bma.beta[1:400,])>0.5))


##ASH
sigmat=(lfsr.ash<thresh)
nsig= rowSums(sigmat)
(signall=mean(het.norm(pm.ash.beta[nsig>0,])>0.5))
(signall.ash=mean(het.norm(pm.ash.beta[1:400,])>0.5))
####SHow that results are robust in specific analysis

(truth=(mean(het.norm(data$beta[1:400,])>0.5)))
(standard=mean(het.norm(data$betahat[1:400,])>0.5))


(RMLE=sqrt(mean((standard-truth)^2)))
(RRMSE.mash=sqrt(mean((signall.mash-truth)^2))/RMLE)
(RRMSE.bma=sqrt(mean((signall.bma-truth)^2))/RMLE)
(RRMSE.ash=sqrt(mean((signall.ash-truth)^2))/RMLE)


rmse.all.table=cbind(mash=RRMSE.mash,bmalite=RRMSE.bma,ash=RRMSE.ash)
barplot(as.numeric(rmse.all.table),main="Shared, Unstructured Effects: Magnitude heterogeneity",
        ylab="relative error (RRMSE)",xlab="Method",col=c("green","blue","red"),names=colnames(rmse.all.table),ylim=c(0,1.5),cex.main=1.5,cex.lab=1,cex.names=1,las=1)


```