---
title: "Untitled"
output: html_document
---
Patterns of consistency. Let's image the most common covariance matrices.
```{r}
covmat=readRDS("../Data/covmatAug13withED.rds")
pis=readRDS("../Data/pisAug13withED.rds")$pihat
z.stat=read.table("../Data/maxz.txt")
pi.mat=matrix(pis,ncol=54,byrow=T)
par(mfrow=c(1,2))
barplot(t(as.matrix(colSums(pi.mat))),names=c((paste0("K",seq(1:54)))),las=2,cex.names=0.5,main="PiHat")
```
We can see that there is lots of loading on the denoised matrices.
```{r}
order(colSums(pi.mat),decreasing = T)
```

We can see that just 5 matrices appear to receive the majority of the prior weight ( `r sum(colSums(pi.mat)[1:5])`) .

```{r important.mats}
important=order(colSums(pi.mat),decreasing = T)[1:5]
```
```{r}
#install.packages("fields")
library(fields)

 lapply(important,function(x){
  sample = covmat[[x]]
 image(sample, axes=F)
 mtext(text=colnames(z.stat), side=2, line=0.3, at=seq(0,1,1/43), las=1, cex=0.4)
 mtext(text=colnames(z.stat), side=1, line=0.3, at=seq(0,1,1/43), las=2, cex=0.4)
 image.plot(sample, legend.only=T)
 title(paste0("Covmat",x))}
 )

```

We can see that the first and most important matrix shows highly correlated genetic effects in brain and that the largest effects are correspondingly also seen in brain:
```{r order of importance}
colnames(z.stat)[order(diag(covmat[[3]]),decreasing = TRUE)][1:10]
barplot(sort(diag(covmat[[3]])/max(diag(covmat[[3]])),decreasing=TRUE),names=colnames(z.stat)[order(diag(covmat[[3]]),decreasing=TRUE)],las=2,col=c(rep("green",11),rep("orange",11),rep("magenta",11),rep("red",11)),main="PriorEffectSize",cex.names = 0.5)
```
I've colored the sizes by those tissues in each quartile.
```{r}
normdag=(diag(covmat[[3]])/max(diag(covmat[[3]])))
quantile(normdag)
name.order=colnames(z.stat)[order(diag(covmat[[3]]))]
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
