---
title: "Tissue effective sample sizes"
author: "Sarah Urbut, Gao Wang, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

Different levels of effect sharing among tissues means that effect
estimates in some tissues gain more precision than others from the
joint analysis. Here we quantify an "effective sample size" (ESS) per
tissue and compare against the actual sample sizes.

Compare the last plot, at the bottom of this page, against
Supplementary Figure 1 in the manuscript.

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, fig.width = 8,
                      fig.height = 4,fig.align = "center",
                      comment = "#")
```

## Load data and mash results

Load some of the results generated from the mas analysis of the GTEx
data, as well as summary statistics (e.g., sample sizes, standard
errors) calculated from the raw GTEx data.

```{r load-results}
missing.tissues <- c(7,8,19,20,24,25,31,34,37)
out     <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")
maxz    <- out$test.z
maxbeta <- out$test.b
qtl.names <- sapply(1:length(rownames(maxz)),
  function(x) unlist(strsplit(rownames(maxz)[x],"[_]"))[[1]])
standard.error.from.z <- as.matrix(maxbeta/maxz)
dat <- read.csv("../data/ExprSampleSize.csv.gz",header = TRUE)
rownames(dat) <- dat[,1]
expr.data <- dat[,-1]
expr.sort <- expr.data[rownames(expr.data)%in%qtl.names,]
a         <- match(qtl.names,rownames(expr.sort))
expr.sort <- expr.sort[a,]
exp.sort  <- expr.sort[,-missing.tissues]
colnames(exp.sort) <- colnames(maxz)
standard.error           <- out$test.s
colnames(standard.error) <- colnames(maxz)
tissue.names             <- colnames(maxz)
```

To draw the the bar charts, we use the colours that are used by
convention used to represent the GTEx tissues in plots.

```{r load-tissue-colors}
gtex.colors <- read.table('../data/GTExColors.txt',sep = '\t',
                          comment.char = '')[-missing.tissues,2]
```

Load the marginal posterior variances.

```{r read-marginal-var}
out <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                     "lite.single.expanded.V1.posterior.rds",sep = "."))
marginal.var <- out$marginal.var
```

## Compute effective sample sizes

Compute the effective sample sizes,

$$n_{jeff} = \frac{s_{j}^2}{\tilde{s_{j}^2}}$$

```{r reorder-again}
original.var <- as.matrix(standard.error.from.z)^2
size         <- as.matrix(exp.sort)
post.var     <- as.matrix(marginal.var) * standard.error.from.z^2
njeffective  <- size * original.var/post.var
increase     <- njeffective/size
```

Next, order the tissues by the actual sample size.

```{r order-by-sample-size}
samplesize          <- apply(size,2,unique)
sampleorder         <- order(samplesize,decreasing = TRUE)
median.nj.effective <- apply(njeffective,2,median)
median.nj.increase  <- apply(increase,2,median)
```

## Plot effective sample sizes

Plot, for each tissue, the effective sample size, and the increase in
the ESS over the actual sample sample size.

```{r plot1, fig.height=5.5, fig.width=8}
par(mfrow=c(1,2))
par(mar=c(5.1,8,4.1,0.1))
barplot(median.nj.effective[sampleorder],cex.names=0.4,las=2,
  col=as.character(gtex.colors[sampleorder]),horiz = TRUE)
title("Median(Nj_effective)",cex.main = 0.8)
par(mar=c(5.1,2,4.1,6))
barplot(median.nj.increase[sampleorder],cex.names=0.4,las=2,
  col=as.character(gtex.colors[sampleorder]),horiz = T,names="",xlim=c(16,0))
title("Median(Nj_effective/Nj_original)",cex.main=0.8)
```

We see that the ESS values are smallest for tissue that show more
"tissue-specific" behaviour (e.g. testis, whole blood), and are
largest for coronary artery, reflecting its stronger correlation with
other tissues.

## Plot effective sample sizes and actual sample sizes

Here we plot the actual sample size and median effective sample size
of each tissue, in which the tissues are ordered by their original
sample size.

```{r plot2, fig.height=5.5, fig.width=8}
par(mfrow = c(1,2))
par(mar = c(5.1,8,1.1,0.1))
barplot(samplesize[sampleorder],cex.names=0.4,las=2,
        col=as.character(gtex.colors[sampleorder]),horiz = TRUE,
        xlim = c(0,2000))
title("Sample Size",cex.main=0.8)
par(mar = c(5.1,2,1.1,6))
barplot(median.nj.effective[sampleorder],cex.names = 0.4,las = 2,
        col = as.character(gtex.colors[sampleorder]),horiz = TRUE,
        names = "",xlim = c(0,2000))
title("Effective Sample Size",cex.main = 0.8)
```

Observe that the effective sample sizes are consistently higher than
actual sample sizes, primarily due to sharing of information among
tissues.
