---
title: "Distribution of eQTL sharing across tissues"
author: "Sarah Urbut, Gao Wang, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

Here we develop another summary of sharing of eQTLs across tissues by
showing the estimated distribution of sharing; specifically, the
distribution of the number of tissues shared by sign and by
magnitude. This complements [this summary](HeterogeneityTables.html)
and [this one](Tspecific.html).

Compare the plots below to the plots in Figure 5 of the paper.

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, fig.width = 8,
                      fig.height = 4,fig.align = "center",
		      comment = "#")
```

## Set up environment

First, we load some functions defined for the mash analyses.

```{r load-functions}
source("../code/normfuncs.R")
```

This is the threshold used to determine whether a gene has an eQTL
in a given tissue.

```{r define-thresh}
thresh <- 0.05
```

## Load data and mash results

Load some GTEx summary statistics, as well as some of the results
generated from the mash analysis of the GTEx data.

```{r load-results}
out     <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")
maxbeta <- out$strong.b
maxz    <- out$strong.z
out <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                     "lite.single.expanded.V1.posterior.rds",sep = "."))
lfsr           <- out$lfsr
pm.mash        <- out$posterior.means
standard.error <- maxbeta/maxz
pm.mash.beta   <- pm.mash * standard.error
```

# Histograms of sharing by magnitude

Sharing by magnitude means that two eQTLs have similar effect size
(within a factor of 2).

The histograms below summarize sharing by magnitude across all tissues
(left), tissues other than brain (middle), and brain tissues only
(right).

```{r hindex-plot-magnitude}
sigmat <- (lfsr <= thresh)
nsig   <- rowSums(sigmat)
par(mar = c(4,4,2,1))
par(oma = c(8,4,0,0) + 0.1)
par(mfrow = c(1,3))
hist((het.func(het.norm(effectsize=pm.mash.beta[nsig>0,]),threshold=0.5)),
     main="",xlab="",breaks=0.5:44.5,col="grey",freq=FALSE,ylim=c(0,0.9),
     xaxt="n")
axis(1,at = seq(1, 44, by=1),labels = c(1:44))
mtext("All Tissues")

sigmat <- (lfsr[,-c(7:16)] <= thresh)
nsig   <- rowSums(sigmat)
hist((het.func(het.norm(effectsize=pm.mash.beta[nsig>0,-c(7:16)]),
     threshold=0.5)),main="",xlab="",breaks=0.5:34.5,col="grey",
     freq=FALSE,ylim=c(0,0.9),xaxt="n")
axis(1,at = seq(1, 34, by=1),labels = c(1:34))
mtext("Non-Brain Tissues")

sigmat     <- (lfsr[,c(7:16)]<=thresh)
nsig       <-  rowSums(sigmat)
brain.norm <- het.norm(effectsize=pm.mash.beta[nsig>0,c(7:16)])
hist(het.func(brain.norm,threshold=0.5),main="",xlab="",breaks=0.5:10.5,
     col="grey",freq=FALSE,xaxt="n",ylim=c(0,0.9))
axis(1, at=seq(1, 10, by=1), labels=c(1:10))
mtext("Brain Tissues")
````

Observe that the distribution of the number of tissues in which an
eQTL is shared by magnitude has a mode at 1. This is a subset of eQTLs
that have much stronger effect in one tissue than in any other
("tissue-specific").

## Histogram of sharing by magnitude

Sharing by sign means that the eQTLs have the same sign of effect.

The histograms below summarize sharing by sign across all tissues
(left), tissues other than brain (middle), and brain tissues only
(right).

````{r hindex-plot-sign}
sign.func <- function (normeffectsize)
  apply(normeffectsize,1,function(x)(sum(x>0)))
sigmat <- (lfsr<=thresh)
nsig   <- rowSums(sigmat)
par(mar = c(4,4.5,2,1))
par(oma = c(8,4,0,0) + 0.1)
par(mfrow = c(1,3))
hist(sign.func(het.norm(effectsize=pm.mash.beta[nsig>0,])),main="",xlab="",
     breaks=0.5:44.5,col="grey",freq=FALSE,xaxt="n",ylim=c(0,0.9))
axis(1, at=seq(1, 44, by=1), labels=c(1:44))
mtext("All Tissues")

sigmat <- (lfsr[,-c(7:16)] <= thresh)
nsig   <- rowSums(sigmat)
hist(sign.func(het.norm(effectsize = pm.mash.beta[nsig>0,-c(7:16)])),
     main="",xlab="",breaks=0.5:34.5,col="grey",freq=FALSE,ylim=c(0,0.9),
     xaxt="n")
axis(1, at=seq(1, 34, by=1), labels=c(1:34))
mtext("Non-Brain Tissues")

sigmat     <- (lfsr[,c(7:16)]<=thresh)
nsig       <-  rowSums(sigmat)
brain.norm <- het.norm(effectsize=pm.mash.beta[nsig>0,c(7:16)])
hist(sign.func(brain.norm),main="",xlab="",breaks=0.5:10.5,col="grey",
     freq=FALSE,xaxt="n",ylim=c(0,0.9))
axis(1, at=seq(1, 10, by=1), labels=c(1:10))
mtext("Brain Tissues")
```

Similar to other summaries of the mash analysis, we see that eQTLs
exhibit a high level of sharing across tissues.
