---
title: "Add appropriate title here."
author: "Sarah Urbut"
output: workflowr::wflow_html
---

*Add text here.*

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, fig.width = 8,
                      fig.height = 4,fig.align = "center",
		      comment = "#")
```

## Set up environment

First, we load some functions defined for the MASH analyses.

```{r load-pkgs, message = FALSE}
source("../workflows/normfuncs.R")
```

## Load data and MASH results

In the next code chunk, we load some GTEx summary statistics, as well
as some of the results generated from the MASH analysis of the GTEx
data.

```{r load-results}
out  <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")
maxb <- out$test.b
maxz <- out$test.z
out  <-readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                    "lite.single.expanded.V1.posterior.rds",sep = "."))
<<<<<<< HEAD
lfsr           <- out$lfsr
pm.mash        <- out$posterior.means
standard.error <- maxbeta/maxz
pm.mash.beta   <- pm.mash * standard.error
pm.mash.nobrain=
  as.matrix(read.table("../output/nobrainposterior.means.txt")[,-1])*
  standard.error[,-c(7:16)]
pm.mash.brain.only=
  as.matrix(read.table("../output/brainonlyposterior.means.txt")[,-1])*
  standard.error[,c(7:16)]
=======
lfsr <- out$lfsr
standard.error <- maxbeta/maxz

pm.mash=read.table("../../Data_vhat/withvhatposterior.means.txt")[,-1]

pm.mash.beta=pm.mash * standard.error
pm.mash.nobrain=as.matrix(read.table("../../withoutbrain/nobrainposterior.means.txt")[,-1])*standard.error[,-c(7:16)]
pm.mash.brain.only=as.matrix(read.table("../../BrainOnly//brainonlyposterior.means.txt")[,-1])*standard.error[,c(7:16)]
>>>>>>> 8c02ce2e437e971cd8ec6cf60c17a943e603874c
```

Let's plot heterogneity by magnitude from the global analysis.

```{r hindexplotmagnitude,echo=FALSE,fig.height=5,fig.width=10}
thresh=0.05
### now make with all tissue effects


par(mar=c(4,4,2,1))
par(oma=c(8,4,0,0) + 0.1)
par(mfrow=c(1,3))


sigmat=(lfsr<=thresh)
nsig= rowSums(sigmat)

hist((het.func(het.norm(effectsize=pm.mash.beta[nsig>0,]),threshold=0.5)),main="",xlab="",breaks=0.5:44.5,col="grey",freq=FALSE,ylim=c(0,0.9),xaxt="n")
axis(1, at=seq(1, 44, by=1), labels=c(1:44))#,ylim=c(0,0.6))#,ylim=c(0,0.6))
mtext("All Tissues")

par(mar=c(4,4,2,1))
sigmat=(lfsr[,-c(7:16)]<=thresh)
nsig= rowSums(sigmat)

hist((het.func(het.norm(effectsize=pm.mash.beta[nsig>0,-c(7:16)]),threshold=0.5)),main="",xlab="",breaks=0.5:34.5,col="grey",freq=FALSE,ylim=c(0,0.9),xaxt="n")
axis(1, at=seq(1, 34, by=1), labels=c(1:34))#,ylim=c(0,0.6))
mtext("Non-Brain Tissues")

par(mar=c(4,4,2,1))
sigmat=(lfsr[,c(7:16)]<=thresh)
nsig= rowSums(sigmat)


brain.norm=het.norm(effectsize=pm.mash.beta[nsig>0,c(7:16)])
hist(het.func(brain.norm,threshold=0.5),main="",xlab="",breaks=0.5:10.5,col="grey",freq=FALSE,xaxt="n",ylim=c(0,0.9))
axis(1, at=seq(1, 10, by=1), labels=c(1:10))
mtext("Brain Tissues")

#title(xlab="Number of Tissues Shared (by magnitude)", outer=TRUE,line=3,cex.lab=3)
````


Now, let's make the same plot with all tissue effects measuring the number of tissues which have a sign equivalent to max effect:


````{r hindexplotsign,echo=FALSE,fig.height=5,fig.width=10}

sign.func=function(normeffectsize){apply(normeffectsize,1,function(x)(sum(x>0)))}
par(mar=c(4,4.5,2,1))
par(oma=c(8,4,0,0) + 0.1)
par(mfrow=c(1,3))



sigmat=(lfsr<=thresh)
nsig= rowSums(sigmat)

hist(sign.func(het.norm(effectsize=pm.mash.beta[nsig>0,])),main="",xlab="",breaks=0.5:44.5,col="grey",freq=FALSE,#ylim=c(0,0.4),
     xaxt="n",ylim=c(0,0.9))
axis(1, at=seq(1, 44, by=1), labels=c(1:44))#,ylim=c(0,0.6))
mtext("All Tissues")


sigmat=(lfsr[,-c(7:16)]<=thresh)
nsig= rowSums(sigmat)

hist((sign.func(het.norm(effectsize=pm.mash.beta[nsig>0,-c(7:16)]))),main="",xlab="",breaks=0.5:34.5,col="grey",freq=FALSE,ylim=c(0,0.9),#ylim=c(0,0.14),
     xaxt="n")
axis(1, at=seq(1, 34, by=1), labels=c(1:34))#,ylim=c(0,0.6))
mtext("Non-Brain Tissues")

sigmat=(lfsr[,c(7:16)]<=thresh)
nsig= rowSums(sigmat)


brain.norm=het.norm(effectsize=pm.mash.beta[nsig>0,c(7:16)])
hist(sign.func(brain.norm),main="",xlab="",breaks=0.5:10.5,col="grey",freq=FALSE,xaxt="n",ylim=c(0,0.9))
axis(1, at=seq(1, 10, by=1), labels=c(1:10))
mtext("Brain Tissues")


```


