---
title: "Number of tissue-specific eQTLs in each tissue"
author: "Sarah Urbut, Gao Wang, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

Despite high average levels of sharing of eQTLs among tissues, mash
also identifies eQTLs that are relatively "tissue-specific". Here we
count the number of "tissue-specific" eQTLs in each tissue.

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, fig.width = 8,
                      fig.height = 6,fig.align = "center",
                      comment = "#")
```

## Set up environment

First, we load some functions defined for mash analyses.

```{r load-functions}
source("../code/normfuncs.R")
```

*Add text here.*

```{r}
thresh <- 0.05
```

## Load data and mash results

Load some GTEx summary statistics, as well as some of the results
generated from the mash analysis of the GTEx data.

```{r load-results}
out <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")
maxb           <- out$test.b
maxz           <- out$test.z
standard.error <- out$test.s
out <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                     "lite.single.expanded.V1.posterior.rds",sep = "."))
pm.mash      <- out$posterior.means
lfsr.mash    <- out$lfsr
pm.mash.beta <- pm.mash * standard.error
```

For the bar chart below, we use the colours that are
conventionally used to represent the GTEx tissues in plots.

```{r load-tissue-colors}
missing.tissues <- c(7,8,19,20,24,25,31,34,37)
color.gtex      <- read.table("../data/GTExColors.txt",sep = '\t',
                              comment.char = '')[-missing.tissues,]
col = as.character(color.gtex[,2])
```

## Compute number of "tissue-specific" effects for each tissue.

We define "tissue-specific" to mean that the effect is
at least 2-fold larger in one tissue than in any other tissue.
 
```{r count-tissue-specific-effects}
nsig                <- rowSums(lfsr.mash < thresh)
pm.mash.beta.norm   <- het.norm(effectsize = pm.mash.beta)
pm.mash.beta.norm   <- pm.mash.beta.norm[nsig > 0,]
lfsr.mash           <- as.matrix(lfsr.mash[nsig > 0,])
colnames(lfsr.mash) <- colnames(maxz)
a         <- which(rowSums(pm.mash.beta.norm > 0.5) == 1)
lfsr.fold <- as.matrix(lfsr.mash[a,])
pm        <- as.matrix(pm.mash.beta.norm[a,])
tspec     <- NULL
for(i in 1:ncol(pm))
  tspec[i] <- sum(pm[,i] > 0.5)
tspec           <- as.matrix(tspec)
rownames(tspec) <- colnames(maxz)
```

## Plot number of "tissue-specific" effects for each tissue

```{r plot-counts}
par(mfrow = c(2,1))
barplot(as.numeric(t(tspec)),las = 2,cex.names = 0.75,col = col,
        names = colnames(lfsr.fold))
```

Testis stands out as the tissue with the most tissue-specific
effects. Other tissues showing stronger-than-average tissue
specificity include skeletal muscle, thyroid and transformed cell
lines (fibroblasts and LCLs).
