---
title: "Correlation patterns from fourth covariance component"
author: "Sarah Urbut, Gao Wang, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

Here we plot the correlation matrix for the fourth covariance
component, which captures some effects that are stronger in Whole
Blood than other tissues.

```{r knitr, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, fig.width = 8,
                      fig.height = 4,fig.align = "center",
                      comment = "#")
```

## Set up environment

First, we load a couple plotting packages used in the code chunks below.

```{r load-pkgs, message = FALSE}
library(lattice)
library(colorRamps)
```

## Load data and MASH results

In the next code chunk, we load some GTEx summary statistics, as well
as some of the results generated from the MASH analysis of the GTEx
data.

```{r load-results}
covmat <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                        "lite.single.expanded.rds",sep = "."))
pis    <- readRDS(paste("../output/MatrixEQTLSumStats.Portable.Z.coved.K3.P3",
                        "lite.single.expanded.V1.pihat.rds",sep = "."))$pihat
z.stat <- readRDS("../data/MatrixEQTLSumStats.Portable.Z.rds")$test.z
pi.mat <- matrix(pis[-length(pis)],ncol = 54,nrow = 22,byrow = TRUE)
names  <- colnames(z.stat)
```

Next, we load the tissue indices:

```{r load-tissues-names}
h <- read.table("../data/uk4rowIndices.txt")[,1]
```

For the plots of the eigenvectors, we load the colours that are
conventionally used to represent the tissues in plots.

```{r load-tissue-colors}
missing.tissues <- c(7,8,19,20,24,25,31,34,37)
color.gtex      <- read.table("../data/GTExColors.txt",sep = '\t',
                              comment.char = '')[-missing.tissues,]
```

Compute the correlations from the $k=4$ covariance matrix.

```{r get-correlations}
k           <- 4
x           <- cov2cor(covmat[[k]])
x[x<0]      <- 0
colnames(x) <- names
rownames(x) <- names
```

## Generate heatmap of Uk4 covariance matrix

Now we produce the heatmap showing the full covariance matrix.

```{r heatmapuk4final, fig.height=10, fig.width=10}
clrs <- colorRampPalette(rev(c("#D73027","#FC8D59","#FEE090","#FFFFBF",
                               "#E0F3F8","#91BFDB","#4575B4")))(64)
lat=x[rev(h),rev(h)]
lat[lower.tri(lat)] <- NA
n=nrow(lat)
print(levelplot(lat[n:1,],col.regions = clrs,xlab = "",ylab = "",
      colorkey = TRUE))
```

## Plot the eigenvector capturing the predominant pattern

The top eigenvector captures the predominant pattern in the Uk4
covariance matrix.

```{r plot-eigenvectors, fig.width = 6, fig.height = 4}
col = as.character(color.gtex[,2])
g=1
v=svd(covmat[[k]])$v[h,]
rownames(v)=colnames(v)=names[h]
par(mar = c(8,4.1,4.1,2.1))
barplot(v[,g]/v[which.max(abs(v[,g])),g],las=2,
        main=paste("Eigenvector",g,"of Uk",k),cex.names = 0.5,
        col=col[h],names=names[h])
````
